---
title: "MakeoverMonday Week 6"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 06 \#MakeoverMonday

The week 06 is differnet from the others. There are no Data in provided in xlsx only in the Tableau foramts 
and the other other differece is that this week the chalange data are realy big . The source is the open data
Portal of Chicago. 

So I thougt: "ok even if I can not do a viz with that amount of data due to my limited computation capacity 
lets try to connect to the datasource and let see what I can do"

The conection itself turned out not that hard but the data download was qiute slow

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
